\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{textcomp}
 
\pagestyle{fancy}
\fancyhf{}
\lfoot{\small References are available on request}
\rfoot{\small \the\year\hspace{6pt}Vladyslav Polovyi}
\renewcommand{\headrulewidth}{0pt}

\input{public}
%\input{private}

\begin{document}
	\begin{center}
		{\huge\bfseries Junior JavaScript Developer} \\[1em]
		{\Large Vladyslav Polovyi} \\[1em]
		\faMapMarker \quad \myaddress
	\end{center}
	\vspace{1em}
	\textit{\faPaperPlane \quad vlad.polovyi@gmail.com} \hspace*{\fill} \textit{\faPhone \quad \myphone} 

	\section*{Personal Statement}
	A motivated and eager to learn new technologies of engineering software solutions. More then one year in web development with JavaScript.

	\section*{Skills}
	\begin{multicols}{2}
	\begin{itemize}
		\item \textbf{Web apps} with JavaScript, JQuery, HTML, CSS, ReactJS, Angular, ExpressJS, REST.
		\item \textbf{Databases} with SQL, NoSQL (MongoDB, Firebase).
		\item \textbf{Bundlers} with Webpack, Gulp.
		\item \textbf{Other} OOP, basics of Java.
		\item \textbf{Version control} with Git.
		\item \textbf{English} with intermediate level.
	\end{itemize}
	\end{multicols}
	
	\section*{Projects}
	\begin{itemize}
		\item {\textbf{EMA prediction service (Diploma)}}  --- Full stack web app as a prediction service for short time periods. The application gives user 			such service as smoothing data by exponential prediction algorithms. Also user able to save experiments to database and restore it to graph if its 			needed.\\[0.2em]
		{\footnotesize Used \{MongoDB, Express, ReactJS, NodeJS\}} \\[0.2em]

		\item {\textbf{React Notes}} --- web application for taking and storing notes with Google
Authentication on client side \\[0.2em]
		{\footnotesize Used \{Firebase, ReactJS, MaterialUI\}} \\[0.2em]

		\item{\textbf{Evaluation of project indicators}} --- web application created to calculate
the economic indicators of a software project and compare them.
		{\footnotesize Used \{Firebase, ReactJS, MaterialUI\}} \\[0.2em]
		
		\item{\textbf{Pre-interview task \textnumero 1}} --- simple .psd template was given. \\[0.2em]
		{\footnotesize Used \{Html, Css, JS\}} \\[0.2em]
		{\footnotesize Github \{https://github.com/Shchoor/test-task\}} \\[0.2em]
		{\footnotesize Page \{https://task-0001.firebaseapp.com\}} \\[0.2em]

		\item{\textbf{Pre-interview task \textnumero 2}} --- it was required to use html, css and javascript only. Access for server was given both for user  registration  and data acquiring. \\[0.2em]
		{\footnotesize Used \{Html, Css, JS\}} \\[0.2em]
		{\footnotesize Github \{https://github.com/Shchoor/FrontEndTask\}} \\[0.2em]
		

	\end{itemize}
	\subsection*{Profiles}
	\begin{tabular}{@{}lll}
		\faGithub & GitHub & \href{https://github.com/Shchoor}{\texttt{github.com/Shchoor}} \\
		\faLinkedin & LinkedIn & \href{https://www.linkedin.com/in/vlad-polovyi-5b076415a/}{\texttt{linkedin.com/in/vlad-polovyi-5b076415a}} \\
		\faStackOverflow & Stack Overflow & \href{https://stackoverflow.com/users/9047972/vlad-polyovyi}{\texttt{stackoverflow.com/users/9047972/vlad-polyovyi}} \\
	\end{tabular}

	\section*{Education}
	\textbf{2014 -- 2018, 2018 -- Present, Bachelor of Software Engineering and Management Information Technologies.
National Technical University «Kharkiv polytechnic institute»}. \\
	Modules included
	\begin{multicols}{2}
	\begin{itemize}
		\item \textbf{English} \textit{(A)}
		\item \textbf{Calculus} \textit{(C)}
		\item \textbf{Fuzzy Technologies} \textit{(A)}
		\item \textbf{Database Modeling} \textit{(C)}
		\item \textbf{Programming} \textit{(A)}
		\item \textbf{Software Testing} \textit{(B)}
		\item \textbf{Software Modeling and Analysis} \textit{(A)}
		\item \textbf{Requirements analysis} \textit{(B)}
	\end{itemize}
	\end{multicols}

	\section*{Experience}
	Do not have commercial experience yet.
	
	
	
\end{document}
